---
title: "Machine Learning Assignment"
author: "Kanchan Vyas"
date: "10/22/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


---

For the week 4 Graded course project of  practical machine learning  using rstudio markdown and knitr 

The analysis Part

Introduction of the project

Databases is collected from Nike band, Fitbit, jawbone, and we will be utilizing collected data for our analysis in this course assignment.

Now in this project, from the data of the accelerometer measure. of the individuals of their different-different class of physical activity

with the help of accessed data, we will be predict whether the individual is doing his exercises properly and the two files comprise testing and train data,  we will basically predict the counting of exercise like the 
order of them as it should be predicted.

firstly of all load the data and  proceed to process  data and after we find exploratory analysis 
prediction for which model to select,
finally for the predicting of the o/p of the testing set


```{r}
library(data.table)
library(mlbench)
library(caret)
library(klaR)
library(randomForest)
library(rattle)
library(rpart)
library(rpart.plot)
library(corrplot)

```
Now we will take data and clean to make it useful to exploring the data. 

```{r}
testUrl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
traUrl  <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"

data_test <- read.csv(url(testUrl))
data_tra <- read.csv(url(traUrl))


```
Cleaning the Data Input

```{r}
training_data <- data_tra[, colSums(is.na(data_tra)) == 0]
testing_data <- data_test[, colSums(is.na(data_test)) == 0]
```
now we will prepare the data for pred. in which we will consider 70%  of the data for the training set and rest of which is thirty percentage of remaining data set to be tested
and testing_data will be used furthaaaer again for the prediction of the 20% percentage of the cases 

```{r}
training_data <- training_data[, -c(1:7)]
testing_data <- testing_data[, -c(1:7)]
dim(training_data)
```

```{r}
set.seed(1234)
datatraining <- createDataPartition(data_tra$classe, p = 0.7, list = FALSE)
training_data <- training_data[datatraining, ]
testing_data <- training_data[-datatraining, ]
dim(training_data)
dim(testing_data)
```
now we will remove the variables that are non zero from set of data which we have taken okayy
```{r}
noneZero <- nearZeroVar(training_data)
training_data <- training_data[, -noneZero]
testing_data <- testing_data[, -noneZero]
dim(training_data)
dim(testing_data)
```


```{r}
plot_cor <- cor(training_data[, -53])
corrplot(plot_cor, order = "FPC", method = "color", type = "upper", tl.cex = 0.8, tl.col = rgb(0, 0, 0))
```

@@ now in this as we can see that the correcttt predictionsss are the ones with the dark colour intersectionnnnn @@

  proceeding for the model building and for this we will use 2 different types of algorithms , trees and random forests for the prediction part oKayyy 

```{r}
set.seed(20000)
tredec <- rpart(classe ~ ., data=training_data, method = "class")
rpart.plot(tredec)
```

now we will be validating our  model  and there we goo yess.. so good
```{r}
modelpre <- predict(tredec, testing_data, type = "class")
#ab <- confusionMatrix(modelpre, testing_data$classe)
#ab
```

```{r}
plot(modelpre)
```

we are going apply two models one by one lastly will apply
the first is  general boosted model and then the second oneis be gbm model for this 
```{r}
set.seed(10000)
ctr_gbm <- trainControl(method = "repeatedcv", number = 5, repeats = 1)
valid_gbm <- train(classe ~ .,data=training_data, method = "gbm", trControl = ctr_gbm, verbose = FALSE)
valid_gbm$finalModel
```


So in this project, we tried to predict the order wise the someone did the exercise, and then we created the analysis in which we did some cross-validation and why I chose this specific way towards approaching and then predicted for 20.
and i have attached the link to GitHub, which contained the HTML and rmd file. Still, due to some unprecedented reason, I could not attach the file, which consisted of the output, so I have attached the pdf file and the rmd file. Please consider the request, and thank you
it was an amazing experience overall
thank you, mentors and university 




